Carcinoma

### 2022-05-16 inst/carcinoma.Rmd
fixes #135

@@

```{r loadlib}
carcinoma_table <- read.table("carcinoma.txt",header=TRUE)
carcinoma_table[,1:7] <- carcinoma_table[,1:7] > 0
wanted <- !(apply(carcinoma_table[,1:7],1,sum) %in% c(0,7))
carcinoma_table <- carcinoma_table[wanted,]
carcinoma_table
```

@@

for(i in seq_len(nrow(carcinoma_table))){
      jj <- unlist(carcinoma_table[i,1:7])
      negative <- names(jj)[jj==0]
      positive <- names(jj)[jj==1]
      Wi[[i]] <- ggrl(W,positive,negative)
}
carcinoma <- lsl(Wi,powers= carcinoma_table$n)
```

@@

```{r,label=countcarcinoma,cache=TRUE}
carcinoma_count <- colSums(sweep(carcinoma_table[,1:7],1,carcinoma_table$n,"*"))
names(carcinoma_count) <- colnames(carcinoma_table)[1:7]
carcinoma_count <- carcinoma_count/sum(carcinoma_count)
carcinoma_count
lc <- loglik_lsl(carcinoma_count,carcinoma)
```

>>>>

Here, the object of inference is the set of pathologists.  Informative

@@

```{r loadlib}
carcinoma_table <- read.table("carcinoma.txt",header=TRUE)
carcinoma_table[,1:7] <- carcinoma_table[,1:7] > 0
carcinoma_table
```

```{r makeshorttable}
wanted <- !(apply(carcinoma_table[,1:7],1,sum) %in% c(0,7))
carcinoma_table_short <- carcinoma_table[wanted,]
```

@@

for(i in seq_len(nrow(carcinoma_table_short))){
      jj <- unlist(carcinoma_table_short[i,1:7])
      negative <- names(jj)[jj==0]
      positive <- names(jj)[jj==1]
      Wi[[i]] <- ggrl(W,positive,negative)
}
carcinoma <- lsl(Wi,powers= carcinoma_table_short$n)
```

@@

```{r,label=countcarcinoma,cache=TRUE}
carcinoma_count <- colSums(sweep(carcinoma_table_short[,1:7],1,carcinoma_table_short$n,"*"))
names(carcinoma_count) <- colnames(carcinoma_table_short)[1:7]
carcinoma_count <- carcinoma_count/sum(carcinoma_count)
carcinoma_count
lc <- loglik_lsl(carcinoma_count,carcinoma)
```
